---
title: Office Ratings
author: ~
date: '2020-12-07'
slug: office-ratings
categories: []
tags: []
---

```{r include = FALSE}
library(here)
library(ggplot2)
library(tidyverse)
library(readxl)
library(schrute)
knitr::opts_chunk$set(echo = FALSE, tidy = TRUE)
```
# Office Ratings

For this project, I am going to be looking at Office Ratings data set contained in the library "schrute" which I installed through R. This data set contains ratings of each episode from the famous US adapted sitcom television series. The data has 55,130 observation and 12 variables. The variable season tells us which season of the show is being selected from. The variable episode tells us which episode of the season is being selected. The variable episode_name tells us the name of the episode. The variable director and writer tells us the director and writer of the episode, respectively. The variable character displays the cahracter that is speaking, and the variable text shows what they said. The variable imdb_rating tell us the rating given for the episode by imdb. The variable total_votes tells us how many people contributed to the imdb_rating; and finally, the variable air_data tells us when that specific episode was aired.

Here is a preview of the data set I am using...

```{r}
dat1 <- schrute::theoffice
glimpse(dat1)
```

# Question 1:
What are the five highest rated episode?

```{r}
results <- dat1 %>%
  select(episode_name, imdb_rating, season, episode) %>%
  group_by(episode_name, season, episode) %>%
  summarise(max_rating = max(imdb_rating, na.rm = TRUE)) %>%
  arrange(desc(max_rating))

results[1:5,]
```
The top 5 rated episodes were the Finale, Goodbye, Michael, Stress Relief (Part1&2), A.A.R.M, and Casino Night ranging from 9.3 to 9.7 which are very good ratings.

# Question 2:
Have the ratings of the seasons changed over time? 

```{r}
season_stats <- dat1 %>%
  group_by(season) %>%
  summarise(mean_rating = mean(imdb_rating))

ggplot(season_stats, aes(x = season, y = mean_rating)) + 
  geom_line() +
  ggtitle("The Office Season Ratings") +
  xlab("Season") +
  ylab("Rating") +
  scale_x_continuous(breaks=seq(1,10,1)) +
  scale_y_continuous(limits=c(7.5,9))
```
From this graphic we can see that the show was slowly rated better and better up to season 4 where it peaked, and then began to fall never surpising 8.5 for the rest of the seasons.

# Question 3:
Which season contains the highest average rating?

```{r}
season_stats <- dat1 %>%
  group_by(season) %>%
  summarise(mean_rating = mean(imdb_rating)) %>%
  arrange(desc(mean_rating))

season_stats[1:9,]
```
From this dataset we can see that the highest rated season is season 4 with an average rating of 8.65/10, we can also see that the lowest rated season is season 8 with an average rating of 7.67/10. This means the range for ratings for The Office is about 1 point. All the seasons wer rated between 7.67 and 8.65.

# Question 4:
Which characters talk the most throughout the show?

```{r}
most_spoken <- dat1 %>%
  group_by(character) %>%
  summarise(count = n()) %>%
  mutate(in_graph = count>250) %>%
  filter(in_graph == TRUE)

ggplot(most_spoken, aes(x = character, y = count)) +
  geom_bar(stat = "identity") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  ggtitle("Most Spoken Characters in the Office") +
  xlab("Character") +
  ylab("Count")
```
From this bar graph yoy can see that the charcter that spoke the most throughout the show was Michael, followed by Dwight, Jim, and then Pam. You could say that these characters are probably the most important, or the "main" characters throughout most of the show.



