---
title: Dogs
author: ~
date: '2020-12-07'
slug: dogs
categories: []
tags: []
---
```{r include = FALSE}
library(here)
library(ggplot2)
library(tidyverse)
library(readxl)
knitr::opts_chunk$set(echo = FALSE, tidy = TRUE)
```

# Dogs

Using the data from TidyTuesdays website, I am going to look at dog descriptions, exporting and importing of dgos, and dogs that have traveled. The first data set contains 58,180 observations and 36 variables. The second data set contains 90 observations and 5 variables. The third data set contains 6,194 observations and 8 variables. From these data sets I can see which dogs are better able to perform tricks, which dogs travel more than other dogs, whether these certain dogs are mixed, or purebred, their colors, sex, size, coat length, and many others. Using this data you can find out quite a bit about certain dog species.

Below is a preview of the data sets I am using for this analysis

```{r}
dat2 <- read.csv(here::here("data", "tidytuesday", "data", "2019", "2019-12-17",
"dog_descriptions.csv"))

dat3 <- read.csv(here::here("data", "tidytuesday", "data", "2019", "2019-12-17",
"dog_moves.csv"))

dat4 <- read.csv(here::here("data", "tidytuesday", "data", "2019", "2019-12-17",
"dog_travel.csv"))
```

```{r}
glimpse(dat2)
glimpse(dat3)
glimpse(dat4)
```

# Question 1:
Which state exports the most dogs? Which state imports the most dogs?

```{r}
max_exported_set <- dat3 %>%
  select(location, exported, imported) %>%
  group_by(location) %>%
  summarise(max_exported = max(exported, na.rm = TRUE)) %>%
  arrange(desc(max_exported))

max_exported_set[1,]
```
From this data you can see that the state in which the most dogs are exported, or in other words, put up from adoption is Texas.
```{r}
max_imported_set <- dat3 %>%
  select(location, exported, imported) %>%
  group_by(location) %>%
  summarise(max_imported = max(imported, na.rm = TRUE)) %>%
  arrange(desc(max_imported))

max_imported_set[1,]
```
From this data you can see that the state that imports or adopts the most dogs is New York.

# Question 2:
Where are dogs found the most? Which states lose the most dogs?
```{r}
found_dogs <- dat4 %>%
  group_by(found) %>%
  summarise(count = n()) %>%
  arrange(desc(count))

found_dogs[1:5,]
```
This data shows us that the top 5 states in which lost dogs are found is, Texas, Alabama, Virginia, North Carolina, Maryland

```{r}
lost_dogs <- dat4 %>%
  group_by(contact_state) %>%
  summarise(count = n()) %>%
  arrange(desc(count))

lost_dogs[1:5,]
```
From this data set we can see that the sates which the lose the most dogs are Virginia, Washington, New Jersey, New York, and Maryland

# Question 3:
What proportion of dogs are pure-bred? Which coat types are more common, and which coat types are less common?

```{r}
bred_pure <- dat2 %>%
  group_by(breed_mixed, count = n()) %>%
  summarise(pure_bred = n()) %>%
  group_by(breed_mixed, count, pure_bred) %>%
  summarise(percent_pure = (pure_bred/count)*100) 

bred_pure
```
The proportion of dogs which are pure-bred is 28.51%, which is a minority. This means that most dogs up for adoption are a mixed breed of some sort.
```{r}
coat_types <- dat2 %>%
  select(coat) %>%
  drop_na(coat) %>%
  group_by(coat) %>%
  summarise(count = n())

ggplot(coat_types, aes(x=coat, y = count))+
  geom_bar(stat = "identity") + 
  ggtitle("Prevalence of Coat Type") +
  xlab("Coat Type") +
  ylab("Count")
```
From this graph you can see that the short and medium coat types are the most common, the Hairless, Curly, Wire, and Long coat types are much more uncommon. 

# Question 4:
What proportion of dogs are seniors? What primary breed is put up for adoption the most?

```{r}
senior_proportion <- dat2 %>%
  mutate(count = n()) %>%
  group_by(age, count) %>%
  drop_na(age) %>%
  summarise(value = n()) %>%
  summarise(percentage = 100*(value/count))

senior_proportion
```
The proportion of dogs up for adoption that are seniors is 7.96% which is the smallest proportion which makes sense because most owners are not going to put old dogs up for adoption. The largest proportion of dogs that are up for adoption are adult dogs.

```{r}
adoption <- dat2 %>%
  drop_na(breed_primary) %>%
  group_by(breed_primary) %>%
  summarise(count = n()) %>%
  mutate(worthy = count > 750) %>%
  filter(worthy == TRUE)

ggplot(adoption, aes(x = breed_primary, y = count)) +
  geom_bar(stat = "identity") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  ggtitle("Dogs for Adoption by Breed") +
  xlab("Primary Breed") +
  ylab("Count")
```
From these graphics we can see that the dog breed put up for adoption most is the PitBull Terrier followed by the Labrador Retriever then the Chihuaua.
