---
title: "Project Proposal"
author: "Braden Fowler"
date: '2020-12-03'
output: pdf_document
categories: []
tags: []
slug: project-proposal
---

My blog is available at https://dasc1104-blog-project.netlify.app/
```{r message = FALSE}
library(here)
library(ggplot2)
library(tidyverse)
library(readxl)
knitr::opts_chunk$set(echo = FALSE, tidy = TRUE)
```

```{r}
dat1 <- read.csv(here::here("data", "tidytuesday", "data", "2020", "2020-03-17",
"office_ratings.csv"))
```

```{r}
glimpse(dat1)
```

For this project, I am goign to be looking at Office Ratings data set contained in the office_ratings.csv file on Tidy Tuesday's website. This data set contains ratings of each episode from the famous US adapted sitcom television series. The data has 188 observation and 6 variables. The variable season tells us which season of the show is being selected from. The variable episode tells us which episode of the season is being selected. The variable title tells us the title of the episode being selected. The variable imdb_rating tell us the rating given for the episode by imdb. The variable total_votes tells us how many people contributed to the imdb_rating; and finally, the variable air_data tells us when that specific episode was aired.

      Question 1:
      Question 2:
      Question 3:
      
```{r}
dat2 <- read.csv(here::here("data", "tidytuesday", "data", "2019", "2019-02-05",
"mortgage.csv"))

dat3 <- read.csv(here::here("data", "tidytuesday", "data", "2019", "2019-02-05", "recessions.csv"))

dat4 <- read.csv(here::here("data", "tidytuesday", "data", "2019", "2019-02-05", "state_hpi.csv"))
```

```{r}
glimpse(dat2)
glimpse(dat3)
glimpse(dat4)
```


      Question 1:
      Question 2:
      Question 3: